Random Forests", OAs

### 2024-09-11 src/la_RF_corrected.Rmd
oa correlations

>>>>

## Correlations

```{r}
cor <- df %>% dplyr::select(n, n.London.lag, n.nearest.city.lag, n.l.slag, year, London, dist) 
cor <- rcorr(as.matrix(cor))
r <- cor$r
p <- cor$P

path.out <- paste0(path, "/outputs/rf/correlations/corr_LAD_corrected.csv")
r %>% as_tibble(rownames = "rowname") %>% 
  write_csv(path.out)

path.out <- paste0(path, "/outputs/rf/correlations/corr_LAD_corrected_p.csv")
p %>% as_tibble(rownames = "rowname") %>% 
  write_csv(path.out)
```

### 2024-09-11 src/la_RF_corrected_10.Rmd
oa correlations

>>>>

## Correlations

```{r}
cor <- df %>% dplyr::select(n, n.London.lag, n.nearest.city.lag, n.l.slag, year, London, dist) 
cor <- rcorr(as.matrix(cor))
r <- cor$r
p <- cor$P

path.out <- paste0(path, "/outputs/rf/correlations/corr_LAD_corrected_10.csv")
r %>% as_tibble(rownames = "rowname") %>% 
  write_csv(path.out)

path.out <- paste0(path, "/outputs/rf/correlations/corr_LAD_corrected_10p.csv")
p %>% as_tibble(rownames = "rowname") %>% 
  write_csv(path.out)
```

### 2024-09-11 src/oa_RF_corrected.Rmd
oa correlations

>>>>

## Correlations

```{r}
cor <- rcorr(as.matrix(df[-(1:3)]))
r <- cor$r
p <- cor$P

path.out <- paste0(path, "/outputs/rf/correlations/corr_OA_corrected.csv")
r %>% as_tibble(rownames = "rowname") %>% 
  write_csv(path.out)

path.out <- paste0(path, "/outputs/rf/correlations/corr_OA_corrected_p.csv")
p %>% as_tibble(rownames = "rowname") %>% 
  write_csv(path.out)
```

### 2024-09-11 src/oa_RF_corrected_10.Rmd
oa correlations

library(tidyverse)
library(rprojroot)
#library(rgdal)
#library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)
library(CAST)

@@

>>>>

library(tidyverse)
library(rprojroot)
#library(rgdal)
#library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)
library(CAST)
library(Hmisc)

@@

## Correlations

```{r}
cor <- rcorr(as.matrix(df[-(1:3)]))
r <- cor$r
p <- cor$P

path.out <- paste0(path, "/outputs/rf/correlations/corr_OA_corrected_10.csv")
r %>% as_tibble(rownames = "rowname") %>% 
  write_csv(path.out)

path.out <- paste0(path, "/outputs/rf/correlations/corr_OA_corrected_10p.csv")
p %>% as_tibble(rownames = "rowname") %>% 
  write_csv(path.out)
```
